Cells at War: The Playfulness of Game-Based Learning

### 2023-04-05 cellsatwar_bus_presentation/beap_pres_dec.tex
Updated pres

% Title page details: 
\title[BEAP Dec 2022]{Cells at War: The Playfulness of Game-Based Learning} 
\author{Alexander Turco}
\date{December 5, 2022}
\logo{\includegraphics[height=1cm, width=1cm]{logo.png}}

@@

	\section{Conclusion}
	\begin{frame}{Conclusions}
		\begin{enumerate}	
			\item Game based learning approaches have the potential to be utilized during lecture as interactive educational tools for students. \newline
			\item Implementing Game-based learning practices could improve student motivation to apply and analyze what they learn, and use it to form new understandings of concepts. \newline
			\item In a cohort where many students did not play video games, learning to play did not distract from understanding the content. \newline
			\item Not only benefits for the students playing the game, but also for the team of students and supervisors from different schools, in different programs, working in collaboration with eachother.
		\end{enumerate}
	\end{frame}

>>>>

% Title page details: 
\title[BEAP Dec 2022]{Cells at War: The Playfulness of Game-Based Learning} 
\author{Alexander Turco}
\date{April 5, 2023}
\logo{\includegraphics[height=1cm, width=1cm]{logo.png}}

@@

	\section{Conclusion}
	\begin{frame}{Conclusions}
		\begin{enumerate}	
			\item Game based learning approaches have the potential to be utilized during lecture as interactive educational tools for students. \newline
			\item Implementing Game-based learning practices could improve student motivation to apply and analyze what they learn, and use it to form new understandings of concepts. \newline
			\item In a cohort where many students did not play video games, learning to play did not distract from understanding the content. \newline
			\item Not only benefits for the students playing the game, but also for the team of students and supervisors from different schools, in different programs, working in collaboration with each other.
		\end{enumerate}
	\end{frame}
